Multisensor Architecture for an Intersection Management System

### 2018-06-12 ch3-arch_sys.tex
Added epigraphe packages and section titles to chapter 3
Fixed list of processing blocks and images

@@

\subsection{Processing Blocks}

@@

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.8]{fig/3/laser_bg_remove.pdf}
\caption{laser\_bg\_remove}
\label{laser_bg_remove}
\end{figure}

@@

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.8]{fig/3/polar2cart.pdf}
\caption{polar\_to\_cartesian}
\label{polar_to_cartesian}
\end{figure}

@@

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.8]{fig/3/laser_cart_merge.pdf}
\caption{laser\_cart\_merge}
\label{laser_cart_merge}
\end{figure}

@@

\item[points\_to\_cluster] \hfill

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.8]{fig/3/points_to_clusters.pdf}
\caption{points\_to\_clusters}
\label{points_to_clusters}
\end{figure}

@@

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.8]{fig/3/points_to_grid.pdf}
\caption{points\_to\_grid}
\label{points_to_grid}
\end{figure}

@@

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.8]{fig/3/grid_to_occupancy_level.pdf}
\caption{grid\_to\_occupancy\_level}
\label{grid_to_occupancy_level}
\end{figure}

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.8]{fig/3/clusters_to_occupancy_level.pdf}
\caption{clusters\_to\_occupancy\_level}
\label{clusters_to_occupancy_level}
\end{figure}

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.7]{fig/3/occupancy_level_merge.pdf}
\caption{occupancy\_level\_merge}
\label{occupancy_level_merge}
\end{figure}

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.7]{fig/3/occupancy_level2int_state.pdf}
\caption{occupancy\_level\_to\_intersection\_state}
\label{occupancy_level2int_state}
\end{figure}

@@

%{laser_background_remove}
\subsubsection{Feature Analysis}
\subsubsection{Pattern Recognition}
\subsubsection{Situation Assesment}
\subsubsection{Tools and Utilities}

>>>>

\epigraph{"Perfect is enemy of good"}{Voltaire}

@@

\subsection{Processing Blocks} \label{proc_blocks}

@@

\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/3/laser_bg_remove.pdf}
\caption{laser\_bg\_remove}
\label{laser_bg_remove}
\end{figure}

@@

\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/3/polar2cart.pdf}
\caption{polar\_to\_cartesian}
\label{polar_to_cartesian}
\end{figure}

@@

\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/3/laser_cart_merge.pdf}
\caption{laser\_cart\_merge}
\label{laser_cart_merge}
\end{figure}

@@

\item[camera\_background\_remove] \hfill

\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/3/camera_bg_remove.pdf}
\caption{camera\_background\_remove block}
\label{cam_bg_remove}
\end{figure}

\subsubsection{Feature Analysis}
\begin{description}
\item[points\_to\_cluster] \hfill

\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/3/points_to_clusters.pdf}
\caption{points\_to\_clusters}
\label{points_to_clusters}
\end{figure}

@@

\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/3/points_to_grid.pdf}
\caption{points\_to\_grid}
\label{points_to_grid}
\end{figure}

@@

\item[occgrid\_merge] \hfill

\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/3/occgrid_merge.pdf}
\caption{occgrid\_merge}
\label{occgrid_merge}
\end{figure}

\item[camera\_blobs] \hfill

\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/3/camera_blobs.pdf}
\caption{camera\_blobs}
\label{camera_blobs}
\end{figure}

\item[camera\_blobs2occgrid] \hfill

\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/3/camera_blobs2occgrid.pdf}
\caption{camera\_blobs2occgrid}
\label{camera_blobs2occgrid}
\end{figure}

@@

\subsubsection{Pattern Recognition}
\begin{description}

\item[clusters\_vehicle\_counter] \hfill

\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/3/clusters_veh_counter.pdf}
\caption{clusters\_vehicle\_counter}
\label{clusters_vehicle_counter}
\end{figure}

\item[clusters\_to\_occupancy\_level] \hfill
\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/3/clusters2occlvl.pdf}
\caption{clusters\_to\_occupancy\_level}
\label{clusters_to_occupancy_level}
\end{figure}

\item[occgrid\_vehicle\_counter] \hfill

\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/3/occgrid_veh_counter.pdf}
\caption{occgrid\_vehicle\_counter}
\label{occgrid_vehicle_counter}
\end{figure}

\item[occgrid\_to\_occupancy\_level] \hfill
\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/3/occgrid2occlvl.pdf}
\caption{occgrid\_to\_occupancy\_level}
\label{occgrid_to_occupancy_level}
\end{figure}

\subsubsection{Situation Assesment}
\begin{description}

\item[vehicle\_counter\_merge] \hfill
\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/3/veh_cnt_merge.pdf}
\caption{vehicle\_counter\_merge}
\label{vehicle_counter_merge}
\end{figure}

\item[occupancy\_level\_merge] \hfill
\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/3/occlvl_merge.pdf}
\caption{occupancy\_level\_merge}
\label{occupancy_level_merge}
\end{figure}

\subsubsection{Tools and Utilities}
\begin{description}

\item[laser\_publisher] \hfill
\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/3/laser_publisher.pdf}
\caption{laser\_publisher}
\label{laser_publisher}
\end{figure}

\item[camera\_publisher] \hfill
\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/3/camera_publisher.pdf}
\caption{camera\_publisher}
\label{camera_publisher}
\end{figure}

\item[dataset\_control] \hfill
\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/3/dataset_ctrl.pdf}
\caption{dataset\_control}
\label{dataset_control}
\end{figure}

\item[data\_viewer] \hfill
\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/3/data_viewer.pdf}
\caption{data\_viewer}
\label{data_viewer}
\end{figure}

\subsection{Conclusions}
